The Rockerverse: Packages and Applications for Containerisation with R

### 2020-08-17 rockerverse.tex
fix Celeste's affiliation
rename bibliography, add zipfile snippet

\href{https://cyverse.org}{CyVerse} is an open-source, NSF-funded
cyberinfrastructure platform for the life sciences providing easy access
to computing and storage resources \citep{merchant_iplant_2016}. CyVerse
has a browser-based `data science workbench' called the
\href{https://cyverse.org/discovery-environment}{Discovery Environment}
(DE). The DE uses a combination of
\href{https://research.cs.wisc.edu/htcondor/}{HTCondor} and Kubernetes
for orchestrating container-based analysis and integrates with external
HPC, i.e., \href{https://www.xsede.org/}{NSF-XSEDE}, through
\href{https://www.tacc.utexas.edu/tapis}{TAPIS}(TACC-API's). CyVerse
hosts a multi-petabyte Data Store based on
\href{https://irods.org/}{iRODS} with shared access by its users. The DE
runs Docker containers on demand, with users able to integrate bespoke
containers from DockerHub or other registries
\citep{devisetty_bringing_2016}. Rocker image integration in the DE is
designed to provide researchers with scalable, compute-intensive, R
analysis capabilities for large and complex datasets (e.g.,
genomics/multi-omics, GWAS, phenotypic data, geospatial data, etc.).
These capabilities give users flexibility similar to Binder, but allow
containers to be run on larger computational resources (RAM, CPU, Disk,
GPU), and for longer periods of time (days to weeks). The Rocker
Project's RStudio and Shiny are integrated into the DE by deriving new
images from Rocker
images\footnote{See \href{https://github.com/cyverse-vice/}{https://github.com/cyverse-vice/} for \texttt{Dockerfile}s and configuration scripts; images are auto-built on DockerHub at \href{https://hub.docker.com/u/cyversevice}{https://hub.docker.com/u/cyversevice}.}.
These new images include a reverse proxy using \texttt{nginx} to handle
communication with CyVerse's authentication system
\citep{rstudio_proxy_2020}; CyVerse also allows owners to invite other
registered users to securely access the same instance. The CyVerse
Rocker images further include tools for connecting to its Data Store,
such as the CLI utility \texttt{icommands} for iRODS. CyVerse accounts
are free (with some limitations for non-US users), and the
\href{https://learning.cyverse.org/}{CyVerse Learning Center} provides
community members with information about the platform, including
training and education opportunities.

@@

DN is supported by the project Opening Reproducible Research
(\href{https://www.uni-muenster.de/forschungaz/project/12343}{o2r})
funded by the German Research Foundation (DFG) under project number
\href{https://gepris.dfg.de/gepris/projekt/415851837}{PE~1632/17-1}. The
funders had no role in data collection and analysis, decision to
publish, or preparation of the manuscript. KR was supported in part by a
grant from The Leona M. and Harry B. Helmsley Charitable Trust, award
number 2016PG-BRI004. LS and NT are supported by US NIH / NHGRI awards
U41HG00405 and U24HG010263. CW is supported by the Whole Tale project
(\url{https://wholetale.org}) funded by the US National Science
Foundation (NSF) under award
\href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1541450}{OAC-1541450}.
NR is supported in part by the Chan-Zuckerberg Initiative Essential Open
Source Software for Science program. We would like to thank Celeste R.
Brennecka from the Science Writing Support Service of the University of
Münster for her editorial support.

\bibliography{RJreferences}

>>>>

\href{https://cyverse.org}{CyVerse} is an open-source, NSF-funded
cyberinfrastructure platform for the life sciences providing easy access
to computing and storage resources \citep{merchant_iplant_2016}. CyVerse
has a browser-based `data science workbench' called the
\href{https://cyverse.org/discovery-environment}{Discovery Environment}
(DE). The DE uses a combination of
\href{https://research.cs.wisc.edu/htcondor/}{HTCondor} and Kubernetes
for orchestrating container-based analysis and integrates with external
HPC, i.e., \href{https://www.xsede.org/}{NSF-XSEDE}, through
\href{https://www.tacc.utexas.edu/tapis}{TAPIS} (TACC-API's). CyVerse
hosts a multi-petabyte Data Store based on
\href{https://irods.org/}{iRODS} with shared access by its users. The DE
runs Docker containers on demand, with users able to integrate bespoke
containers from DockerHub or other registries
\citep{devisetty_bringing_2016}. Rocker image integration in the DE is
designed to provide researchers with scalable, compute-intensive, R
analysis capabilities for large and complex datasets (e.g.,
genomics/multi-omics, GWAS, phenotypic data, geospatial data, etc.).
These capabilities give users flexibility similar to Binder, but allow
containers to be run on larger computational resources (RAM, CPU, Disk,
GPU), and for longer periods of time (days to weeks). The Rocker
Project's RStudio and Shiny are integrated into the DE by deriving new
images from Rocker
images\footnote{See \href{https://github.com/cyverse-vice/}{https://github.com/cyverse-vice/} for \texttt{Dockerfile}s and configuration scripts; images are auto-built on DockerHub at \href{https://hub.docker.com/u/cyversevice}{https://hub.docker.com/u/cyversevice}.}.
These new images include a reverse proxy using \texttt{nginx} to handle
communication with CyVerse's authentication system
\citep{rstudio_proxy_2020}; CyVerse also allows owners to invite other
registered users to securely access the same instance. The CyVerse
Rocker images further include tools for connecting to its Data Store,
such as the CLI utility \texttt{icommands} for iRODS. CyVerse accounts
are free (with some limitations for non-US users), and the
\href{https://learning.cyverse.org/}{CyVerse Learning Center} provides
community members with information about the platform, including
training and education opportunities.

@@

DN is supported by the project Opening Reproducible Research
(\href{https://www.uni-muenster.de/forschungaz/project/12343}{o2r})
funded by the German Research Foundation (DFG) under project number
\href{https://gepris.dfg.de/gepris/projekt/415851837}{PE~1632/17-1}. The
funders had no role in data collection and analysis, decision to
publish, or preparation of the manuscript. KR was supported in part by a
grant from The Leona M. and Harry B. Helmsley Charitable Trust, award
number 2016PG-BRI004. LS and NT are supported by US NIH / NHGRI awards
U41HG00405 and U24HG010263. CW is supported by the Whole Tale project
(\url{https://wholetale.org}) funded by the US National Science
Foundation (NSF) under award
\href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1541450}{OAC-1541450}.
NR is supported in part by the Chan-Zuckerberg Initiative Essential Open
Source Software for Science program. We would like to thank Celeste R.
Brennecka from the Scientific Editing Service of the University of
Münster for her editorial support.

\bibliography{rockerverse}
